\vfill A Testing Framework for Web Applications

### 2014-02-26 Paper/paper.tex
Minor Travis addition/rewrite.

Travis requires that you projects be hosted on GitHub, but by doing so the setup is incredibly easy. You sign into Travis using your GitHub credentials and Travis pulls up all of your repositories automatically. Getting a project running with Travis is fairly easy; you create a yml file in your repository, I was able to set up everything I needed in six very simple lines.

>>>>

Travis requires that your projects be hosted on GitHub, but by doing so the setup is incredibly easy. You sign into Travis using your GitHub credentials and Travis pulls up all of your repositories automatically. Getting a project running with Travis is fairly easy; you just create a yml file in your repository. I was able to set up everything I needed in six very simple lines.
